---
title: "Visualizing song lyrics"
author: "Katelyn Chang"
date: "02-13-2020"
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
---

```{r set-up, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

# Getting started

1. Clone your repo `appex06-[github_name]` to create a new project
   in RStudio Cloud under the STA 199 class space.

2. Configure git
      ```{r config-git-ex, eval=FALSE}
      library(usethis)
      use_git_config(user.name="your name", user.email="your email")
      ```

# Packages and Data

We'll make use of the following packages.

```{r load-packages}
library(tidyverse)
library(tidytext)
library(genius) # https://github.com/JosiahParry/genius
library(wordcloud)
library(reshape2)
```

## Part 1

Choose two albums of your choice, and read in their song lyric data from Genius.
Add a variable for the artist and album, and don't forget to save these data 
frames for later use. 

```{r part-1-reading-data}
ariana <- genius_album(
  artist = "Ariana Grande", 
  album = "thank you, next"
  )
ariana2 <- genius_album(
  artist = "Ariana Grande", 
  album = "Yours Truly"
  )
```
```{r}
ariana %>%
  distinct(track_title)
ariana2 %>%
  distinct(track_title)
```


## Part 2

Tidy up the lyrics by removing commonly used words. Display a table of the most
commonly used words (after cleaning up the stop words). Are these words what
you expect from the albums? Create a visualization of these words for each 
album.

```{r part-2-cleanup-dataviz}
ariana_lyrics <- ariana %>%
  unnest_tokens(word, lyric)
ariana2_lyrics <- ariana2 %>%
  unnest_tokens(word, lyric)

ariana_lyrics %>%
  anti_join(get_stopwords(source = "smart")) %>%
  count(word) %>%
  arrange(desc(n))

ariana2_lyrics %>%
  anti_join(get_stopwords(source = "smart")) %>%
  count(word) %>%
  arrange(desc(n))

ggplot(ariana_lyrics, aes(fct_reorder(word, n), n)) +
    geom_col() +
    coord_flip() + 
    theme_minimal(base_size = 12) +
    labs(title = "Frequency of 'thank u, next' lyrics", y = "", x = "")

```

## Part 3

Use the `bing` lexicon to get the sentiments for the lyrics for each of your
selected albums. You may need to interactively download this lexicon (I will
demonstrate on the screen; dont forget to change `eval` to be `TRUE` in the
chunk below). Create a visualization comparing positive vs. negative words for 
each album. What comparisons can be made?

```{r part-3-get-lexicon, eval = FALSE}
get_sentiments("bing") 
```

```{r part-3-sentiment-viz}

```

## Part 4

Create a wordcloud for each album.

```{r task-4-wordcloud}

```

# Submission

## Stage, commit and push

1. Stage your modified files.
2. Commit your changes with an informative message.
3. Push your changes to your GitHub repo.
4. Verify your files were updated on GitHub.

# References

1. Perry, J. Package `genius` for scraping song lyrics using the Genius.com API.
https://github.com/JosiahParry/genius
